### 2021-04-01 input/abstract.tex
abstract first draft

\begin{abstract}

  Fog infrastructures allows content providers to better distribute
  data over autonomous systems, hence improving on quality of user
  experience by reducing latency. However, locating the closest data
  sources can prove challenging in dynamic networks with dynamic
  sources. Locating sources may effectively take more time than
  actually downloading contents. \TODO{Related work ?} In this paper,
  we introduce \NAME, a reactive protocol for dynamic logical
  partitioning in dynamic networks. \TODO{source automatically create
    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
    flooding}). \TODO{costs of operations.} When the system becomes
  quiescent, every process eventually converges to its closest
  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
    testbed?}

@@

>>>>

\begin{abstract}
%% Context and problem
  Edge infrastructures have been proposed as an alternative to Cloud
  Computing to provide computing and storage capabilities closer to
  the locations where data is generated/consumed, with the objectives
  of reducing the latency and the volume of data passing through the
  network. A few systems have been proposed to store data in those
  infrastructures. Unfortunately, locating the closest copy of a
  specific content in these systems requires to keep up-to-date an index
  of all replicas and their respective locations. While flooding
  approaches will not enable the maintenance of such an index for each
  node in large systems, relying on a dedicated service contradicts
  with the properties of Edge infrastructures in terms of locality and
  robustness (locating sources may effectively take more time than
  actually downloading contents).

%%% Our proposal
  In this paper, we introduce \NAME, an efficient broadcast protocol
  that relies on dynamic logical partitioning of the
  infrastructure. \NAME only floods the relevant nodes (\ie the ones
  that should be informed of a the creation of a closest copy),
  enabling to keep up-to-date an index for each node eventually.  In
  addition to demonstrating formally the correctness of our protocol \TODO{Is it true?},
  we discuss several evaluatons performed by simulations and show
  \TODO{blabla}.  While \NAME tackles our location problem, it can be
  used as a building block to design new advanced services such as
  \TODO{blabla}.

@@

%\TODO{source automatically create
%    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
%    flooding}). \TODO{costs of operations.} When the system becomes
%  quiescent, every process eventually converges to its closest
%  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
%+    testbed?}
